Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-11-18 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Changes in State of the art

The fulfillment of these properties could be achieved by using any of the
languages and associated technologies, mentioned above, provided that the user had
installed the required virtual machine plugin first, 
% (Paloma) These should be separate sentences
but embedding a
distributed computation client in the browser has the advantage of
providing a single and universal way of accessing resources via an
URI, something that is not guaranteed by using desktop
applications. Baratloo et al. tried in 1996 to create a system with
the aforementioned qualities called {\em Charlotte}
\cite{baratloo1996charlotte}. This system, which implemented a
distributed shared memory, was inspired by a previous work
on parallel computing systems PVM and MPI and solved most of the issues by
using the Java virtual machine embedded in the browser,
which provided
security to the user, uniformity of computing environment
independently of the operating system, and access to a common data store in the
server. Since the Java virtual machine is a sandbox, it is safe to the user
and as it runs compiled bytecode it also guarantees a certain level of
performance.
Other issues such as scheduling, which are related to adaptive 
parallelism, were solved on the server. This
paper was later extended and published in a journal in 1999
\cite{baratloo1999charlotte}, but it is interesting to note that
already in the early stages of the web the possibility of
% (Paloma) Re-write. For example, "but it is interesting to note that, even in the early stages of the web, the possibility of..."
browser-based distributed computing was already researched.

Other systems, like JET, proposed by Soares et
al. \cite{soares1998get}, also used Java. JET supports
the execution of parallel applications over the Internet and features
a comprehensive statistics collection subsystem, allowing its use for science,
since it allows % (Paloma) Use synonyms, like "yield" or "permit"
 the collection of algorithm analytics by the
experiment designer, unlike the other systems mentioned
above. Other proposals contemporary to JET, such as {\em SuperWeb}
\cite{alexandrov1997superweb} are roughly a translation of classical
distribution techniques, with overly complicated architectures that include
brokers for resource discovery. It is focused
% (Paloma) Careful with starting using plural ("Other proposals", "are") and continuig with singular. If you are referring to "SuperWeb", change "It" for "SuperWeb"
, however, in solving the
issues involved in browser-based computing and also in making a system
that is able to work across different types of computers, mentioning
SPARCstations and PCs with Windows-95. Interestingly enough, this
paper incorporates a discussion on the economic model, paving the way
for the for-profit distributed computing systems that arose later on. 
On the other hand, the potential for volunteer computing using
browsers was realized
later on \cite{sarmenta-bayanihan} as well as the potential for
mischief of users with code in their hands
% (Paloma) I think this sentence is extremely informal
\cite{sarmenta-sabotagetolerance}. However, these early efforts by
Sarmenta once again used Java and not JavaScript, making this effort % (Paloma) making them
less widespread.

>>>>

The fulfillment of these properties could be achieved by using any of the
languages and associated technologies, mentioned above, provided that the user had
installed the required virtual machine plugin first. 
% (Paloma) These should be separate sentences
However, embedding a
distributed computation client in the browser has the advantage of
providing a single and universal way of accessing resources via an
URI, something that is not guaranteed by using desktop
applications. Baratloo et al. tried in 1996 to create a system with
the aforementioned qualities called {\em Charlotte}
\cite{baratloo1996charlotte}. This system, which implemented a
distributed shared memory, was inspired by a previous work
on parallel computing systems PVM and MPI and solved most of the issues by
using the Java virtual machine embedded in the browser,
which provided
security to the user, uniformity of computing environment
independently of the operating system, and access to a common data store in the
server. Since the Java virtual machine is a sandbox, it is safe to the user
and as it runs compiled bytecode it also guarantees a certain level of
performance.
Other issues such as scheduling, which are related to adaptive 
parallelism, were solved on the server. This
paper was later extended and published in a journal in 1999
\cite{baratloo1999charlotte}, but it is interesting to note that, even in the early stages of the web, the possibility of 
% (Paloma) Re-write. For example, "but it is interesting to note that, even in the early stages of the web, the possibility of..."
browser-based distributed computing was already researched.

Other systems, like JET, proposed by Soares et
al. \cite{soares1998get}, also used Java. JET supports
the execution of parallel applications over the Internet and features
a comprehensive statistics collection subsystem, allowing its use for science,
since it yields % (Paloma) Use synonyms, like "yield" or "permit". Repetitive use of "allow" is... repetitive.
 the collection of algorithm analytics by the
experiment designer, unlike the other systems mentioned
above. Other proposals contemporary to JET, such as {\em SuperWeb}
\cite{alexandrov1997superweb} are roughly a translation of classical
distribution techniques, with overly complicated architectures that include
brokers for resource discovery. It is focused
% (Paloma) Careful with starting using plural ("Other proposals", "are") and continuig with singular. If you are referring to "SuperWeb", change "It" for "SuperWeb"
, however, in solving the
issues involved in browser-based computing and also in making a system
that is able to work across different types of computers, mentioning
SPARCstations and PCs with Windows-95. Interestingly enough, this
paper incorporates a discussion on the economic model, paving the way
for the for-profit distributed computing systems that arose later on. 
On the other hand, the potential for volunteer computing using
browsers was realized
later on \cite{sarmenta-bayanihan} as well as the potential for
mischief of users with code in their hands
% (Paloma) I think this sentence is extremely informal
\cite{sarmenta-sabotagetolerance}. However, these early efforts by
Sarmenta once again used Java and not JavaScript, making this effort % (Paloma) making them
less widespread.
